CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-23 paper/ms.tex
Fix Fisher matrix calc

\subsection{Something} \label{ssec:co_}
\beq\label{eq:co_fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} 
V_{\text{surv}} \sum_{l} \sum_{m} 
\frac{\partial \hat{P}_l(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} 
\frac{\partial \hat{P}_m(k)}{\partial B_j}\text{,}
\eeq
\eeq
\eeq
\eeq

>>>>

\subsection{Something} \label{ssec:co_}
We now consider the prospects of measuring the \CO{} transition using a
multi-field approach. First, we choose to label each line with the upper
transitional level, e.g. CO(3-2) is referred to as ``3.'' The relevant Fisher
matrix is then,
\beq\label{eq:co_fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $i$ and $j$ each refer to a line by its upper transitional level and the
$l$, $l'$, $m$ and $m'$ sum over all lines considered.

Ignoring interlopers and foreground contamination for a moment, we can
simplify this expression as
\beq\label{eq:fisher_nocontam}
\begin{split}
F_{i,j} =&
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} \denps^2(k) \\
\times & \left[ 
\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
+ \delta_{ij} \left( 
\sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
+ \frac{1}{\pstot{i}\xps{\delta}{\delta} + \xps{i}{\delta}^2}
\right) \right. \\
& + (1-\delta_{ij}) \left(
\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
+ \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
+ \frac{B_iB_j}{\xps{i}{j}^2 + \pstot{i}\pstot{j}}
\right)
\Bigg]
\end{split}
\eeq
